On the properties of discs around accreting brown dwarfs

### 2010-05-26 BD_disc/paper.tex
Still struggling with the inner edge stuff
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2286 25464f21-6099-402c-b30a-640f1d40d38b

**GOT HERE NEED NEW FIGURE FOR INNER EDGE, ALSO REVERSE ARGUMENTS**

@@

Figure \ref{flare_inner} shows the total SEDs for the BDD system of
Figures \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
bottom panels respectively. The left panels show the flux over all the
ten inclinations (see Table \ref{par_space_table}), with the dashed
line showing the inclination at which a sharp fall in flux is
seen. This inclination will be the angle at which the star and inner
disc becomes obscured by the flared outer disc. These inclinations are
71$^{\circ}$ and 56$^{\circ}$ for \logmdot = $-$12 and $-$7
respectively. This effectively means that for higher accretion rates a
more significant fraction of the stars, in a given population, may
have flux below a threshold detection limit. The right panel of Figure
\ref{flare_inner} shows the angles of 0, 27, 39, and 48 $^{\circ}$,
close to face on. Comparing the top and bottom panel show that flux
levels for the higher accretion rate, with the larger and curved inner
edge, vary more distinctly with inclination angle than the systems
with a vertical wall. These trends although demonstrated for one
subset are apparent throughout the grid, i.e.e for each mass and
age. Whilst this effect is probably artificially enhanced for such
extreme accretion rates it is illustrative of the general trend,
notwithstanding complications from inner edge shape.

@@

XXXNOT SURE ABOUT THIS NEXT BIT, PERHAPS A LITTLE WEAKXXX

The lowest panel of Figure \ref{flare_inner_mag} shows the difference
in the inclination dependence of the IR colour for large curved
(\logmdot = $-$7) and smaller vertical (\logmdot = $-$12) inner walls. The
$(J-K)_0$ colour of the higher accretion rate system changes more as a
function of inclination when compared to the lower accretion rate
system. A total change in $(J-K)_0$ of $\approx$ 0.05 and 0.1 are
found for \logmdot = $-$12 and $-$7 respectively. This doubling in the
change in IR colour as a function of inclination for viewing angles
close to face-on, is caused by the larger (vertically) and convex
inner wall in the extreme accreting case. For the convex inner wall
the effective emitting area one observes changes as a function of
inclination, leading to this greater dependence of IR colour on
inclination.

@@

Subsequently, the SEDs of BDD systems with typical accretion rates and
associated discs, are changed significantly from the assumed
underlying photospheric model flux, and therefore become difficult to
classify. In Section \ref{observables} we have shown that the BD
photosphere becomes veiled by the accretion flux for rates of
\logmdot$>-$9. The outer disc flaring observed in the BDD systems was
shown to cause occultation and a subsequent, sharp, fall in flux at an
inclination which decreases for more systems with higher accretion
rates. We have also shown that for extreme accretion rates the inner
wall increases in size and becomes convex in shape. We have also shown
that this leads to a greater dependence on inclination (at
inclinations close to face-on) of the IR colours.

Subsequent derivation of photomertric magnitudes has allowed us to
demonstrate that, as expected, increased accretion without disc
presence, moves our naked systems to bluer and brighter magnitudes.
Once a disc is added the increase in accretion flux interacts with the
disc and does not necessarily lead to a simple motion toward brighter
magnitudes and bluer colours. The increased flaring and obscuration
present in BDD systems, over CTTS, leads to rapid falls in magnitude
with inclination as an accretion (or flaring) dependent inclination.
Furthermore, the disc inner edge leads to a shift redwards with
increasing accretion rate as more flux is intercepted by the inner
edge and the inner edge becomes convex and `puffed up'.

>>>>

**GOT HERE NEED NEW FIGURE FOR INNER EDGE AND NUMBERS WRONG***
CHANGE flareinner.ps and flareinnermag.ps

@@

Figure \ref{flare_inner} shows the total SEDs for the BDD system of
Figures \ref{flare_-12_183} and \ref{flare_-7_193} as the top and
bottom panels respectively. The left panels show the flux over all the
ten inclinations (see Table \ref{par_space_table}), with the dashed
line showing the inclination at which a sharp fall in flux is
seen. This inclination will be the angle at which the star and inner
disc becomes obscured by the flared outer disc. These inclinations are
71$^{\circ}$ and 56$^{\circ}$ for \logmdot = $-$12 and $-$7
respectively. This effectively means that for higher accretion rates a
more significant fraction of the stars, in a given population, may
have flux below a threshold detection limit. The right panel of Figure
\ref{flare_inner} shows the angles of 0, 27, 39, and 48 $^{\circ}$,
close to face on. Comparing the top and bottom panel show that flux
levels for the higher accretion rate, with the larger and curved inner
edge, vary less distinctly with inclination angle than the systems
with a vertical wall. These trends although demonstrated for one
subset are apparent throughout the grid, i.e. for each mass and age.

@@

XXXNOT SURE ABOUT THIS NEXT BIT, PERHAPS A LITTLE WEAKXXX
**SENSE OF ARGUMENT RIGHT BUT NUMBERS WRONG***

The lowest panel of Figure \ref{flare_inner_mag} shows the difference
in the inclination dependence of the IR colour for large curved
(\logmdot = $-$7) and smaller vertical (\logmdot = $-$12) inner
walls. The $(J-K)_0$ colour of the higher accretion rate system
changes less as a function of inclination when compared to the lower
accretion rate system. A total change in $(J-K)_0$ of $\approx$ 0.05
and 0.1 are found for \logmdot = $-$12 and $-$7 respectively. This
halving in the change in IR colour as a function of inclination for
viewing angles close to face-on, is caused by the larger (vertically)
and convex inner wall in the extreme accreting case. For the convex
inner wall the effective emitting area one observes does not change as
much as a vertical wall as a function of inclination, leading to this
reduced dependence of IR colour on inclination.

@@

Subsequently, the SEDs of BDD systems with typical accretion rates and
associated discs, are changed significantly from the assumed
underlying photospheric model flux, and therefore become difficult to
classify. In Section \ref{observables} we have shown that the BD
photosphere becomes veiled by the accretion flux for rates of
\logmdot$>-$9. The outer disc flaring observed in the BDD systems was
shown to cause occultation and a subsequent, sharp, fall in flux at an
inclination which decreases for more systems with higher accretion
rates. We have also shown that for extreme accretion rates the inner
wall increases in size and becomes convex in shape. We have also shown
that this leads to a reducedq dependence on inclination (at
inclinations close to face-on) of the IR colours, compared to a
vertical wall.

Subsequent derivation of photometric magnitudes has allowed us to
demonstrate that, as expected, increased accretion without disc
presence, moves our naked systems to bluer and brighter magnitudes.
Once a disc is added the increase in accretion flux interacts with the
disc and does not necessarily lead to a simple motion toward brighter
magnitudes and bluer colours. The increased flaring and obscuration
present in BDD systems, over CTTS, leads to rapid falls in magnitude
with inclination as an accretion (or flaring) dependent inclination.
Furthermore, the disc inner edge leads to a shift redwards with
increasing accretion rate as more flux is intercepted by the inner
edge and the inner edge becomes convex and `puffed up'.
